---
title: "Data analysis"
author: "D. Mendez"
date: "31/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary
In this project, the goal is to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. I'll be using the train set to train a model that will give me predictions on the test data set.

## Data treatment

I'll download the data and store it appropiately. Moreover, the classe variable is transformed to a factor.

```{r, include=FALSE}
library(dplyr)
trainUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
training <- as_tibble(read.csv(url(trainUrl)))
testing <- as_tibble(read.csv(url(testUrl)))
training$classe <- factor(training$classe)
```

## Preliminary study

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
