---
title: "Pred Assignment"
author: "D. Mendez"
date: "02/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary
In this project, the goal is to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. I'll be using the train set to train a model that will give me predictions on the test data set.

## Data treatment

I'll download the data and store it appropiately. Moreover, the classe variable is transformed to a factor.

```{r, include=FALSE}
library(dplyr); library(caret)
trainUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
training <- as_tibble(read.csv(url(trainUrl)))
testing <- as_tibble(read.csv(url(testUrl)))

```

## Preliminary study

Looking at the data, 42% of the variables are more than 95% NAs and 23% have a NA variance

```{r, include=FALSE}
trainData <- training[!sapply(training, var) %in% c(0, NA)]
trainData$classe <- factor(training$classe)

```

## Fit the model

A random forest method is used. A couple of settings are added to allow for the model to perform fast.

```{r, include=FALSE}

model <- train(classe~.,
               data=trainData,
               preProcess='pca',
               model="rf",
               tuneGrid=data.frame(mtry=3))
```

## Assestment of the model

Checking the confusion matrix we can asses how good the model is

```{r}
print(confusionMatrix(model))
```

Based on the results, the average accuracy of the model is 99.12% which is good enough.

## Code
```{r,eval=FALSE}
library(dplyr); library(caret)
trainUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
training <- as_tibble(read.csv(url(trainUrl)))
testing <- as_tibble(read.csv(url(testUrl)))
trainData <- training[!sapply(training, var) %in% c(0, NA)]
trainData$classe <- factor(training$classe)

model <- train(classe~.,
               data=trainData,
               preProcess='pca',
               model="rf",
               tuneGrid=data.frame(mtry=3))
print(confusionMatrix(model))


```

